Dynein project log

### 2017-01-08 thesis_stuff/thesis_stuff.tex
minor commit on finding spring constants from an experimental motor angle distribution.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess\\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
\end{center}

@@

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
\end{center}

@@

\textbf{Could we use the angle distribution histograms in \ref{fig:EM-angles-burgess} fit to a boltzmann factor with a spring energy to get cm?}

\begin{figure}[h!]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/axonemal-motor-angles.jpg}
  \caption{Angle histograms from EM microscopy on axonemal (not cytoplasmic) dynein.}
  \label{fig:EM-angles-burgess}
\end{figure}
